---
output: github_document
bibliography: references.bib
csl: green-finance.csl
link-citations: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# China Electric Power Sector Province-level Model

<!-- badges: start -->
<!-- badges: end -->

This R-package is a reproduction of CEPRO model, developed in the study [@LUGOVOY2021105176] to evaluate energy transition options for China's electric power sector by the mid-century . The current version CEPRO2.0 is an improved with finer resolution of renewable energy, and is adjusted to the new developments of energyRt modeling package. 

## Installation

You can install the development version of CEPRO from [GitHub](https://github.com/) with:

```{r, eval=F}
# install.packages("devtools")
devtools::install_github("energyRt/energyRt", ref = "dev")
devtools::install_github("energyRt/CEPRO")

```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval=F}
library(energyRt)
library(CEPRO)
## basic example code
```

[tbc...]

## References

